---
title: "Introduction to Statistical Methods"
subtitle: "Academic Theme — Full Feature Showcase"
format:
  dtslides-revealjs:
    slide-number: c/t
    chalkboard: true
bibliography: example-refs.bib
author:
  - name: Your Name
    orcid: 0000-0000-0000-0000
    email: alias@email.com
    affiliations: Department of Statistics
date: last-modified
execute:
  echo: true
---

## Overview

This presentation demonstrates the **academic** theme — a clean, neutral design suitable for any institution.

- Navy/slate color palette
- No institutional branding
- Same feature set as the UNM theme

# Typography & Basics {.section-slide}

## Text Formatting

Standard Markdown formatting works seamlessly:

- **Bold text** for emphasis
- *Italic text* for nuance
- ~~Strikethrough~~ for deletions
- `Inline code` for technical terms like `lm()` or `ggplot2`
- [Links to resources](https://quarto.org)

> "All models are wrong, but some are useful." — George Box

## Lists & Fragments

Use `::: {.fragment}` to reveal items one at a time:

::: {.fragment}
1. State the null hypothesis $H_0$
:::
::: {.fragment}
2. Choose a significance level $\alpha$
:::
::: {.fragment}
3. Compute the test statistic
:::
::: {.fragment}
4. Compare to critical value or compute $p$-value
:::

## Incremental Lists

Add `{.incremental}` to auto-fragment every bullet:

::: {.incremental}
- Assumption checking
- Model fitting
- Diagnostics
- Interpretation
:::

## Font Sizing Utilities {.small-slide}

Apply size classes to spans or divs:

::::: {.columns}
:::: {.column width="50%"}
- [`.largest`]{.largest} (1.20em)
- [`.larger`]{.larger} (1.50em)
- [`.large`]{.large} (1.25em)
- Normal text (1em)
- [`.small`]{.small} (0.80em)
- [`.smaller`]{.smaller} (0.64em)
- [`.smallest`]{.smallest} (0.512em)
::::
:::: {.column width="50%"}
Code blocks scale too:

::: {.small}
```r
# .small code block
summary(lm(y ~ x))
```
:::
::::
:::::

# Slide Types {.section-slide}

## Small Slide {.small-slide}

Use `{.small-slide}` for slides with more content (80% font size).

- Useful when you need to fit slightly more text
- Keeps readability while increasing density
- Great for summary or review slides

## Tiny Slide {.tiny-slide}

Use `{.tiny-slide}` for very dense information (40% font size).

1. Reference lists
2. Detailed code output
3. Appendix material
4. Supplementary tables
5. Method details
6. Full regression output
7. Assumption checks
8. Sensitivity analyses
9. Additional citations
10. Technical notes

## Quote Slide {.quote-slide}

> "The best thing about being a statistician is that you get to play in everyone's backyard."

— John Tukey

## Scrollable Slide {.scrollable}

Add `{.scrollable}` to the slide title for long content.

```{r}
set.seed(42)
n <- 200
x1 <- rnorm(n)
x2 <- rnorm(n)
x3 <- rnorm(n)
y <- 3 + 2*x1 - 1.5*x2 + 0.8*x3 + rnorm(n)
fit <- lm(y ~ x1 + x2 + x3)
summary(fit)
confint(fit)
```

# Layouts {.section-slide}

## Two Columns

::::: {.columns}
:::: {.column width="50%"}
### Left Column

- Regression assumptions
- Linearity
- Normality of residuals
- Homoscedasticity
::::

:::: {.column width="50%"}
### Right Column

- Diagnostic tools
- Residual plots
- Q-Q plots
- Cook's distance
::::
:::::

## Columns with Code & Output

::::: {.columns}
:::: {.column width="50%"}
**The Model**

We fit a simple linear regression:

$$\hat{y} = b_0 + b_1 x$$

where $b_0$ and $b_1$ are estimated via OLS.
::::

:::: {.column width="50%"}
```{r}
#| echo: true
#| fig-height: 4
set.seed(42)
x <- rnorm(50)
y <- 2 + 3*x + rnorm(50)
plot(x, y, pch = 19,
     col = "#4A6FA5")
abline(lm(y ~ x),
       col = "#1B365D", lwd = 2)
```
::::
:::::

## Tabsets

::: {.panel-tabset}
### Summary Stats

```{r}
summary(mtcars[, c("mpg", "hp", "wt")])
```

### Correlation

```{r}
round(cor(mtcars[, c("mpg", "hp", "wt")]), 3)
```

### Model

```{r}
coef(summary(lm(mpg ~ hp + wt, data = mtcars)))
```
:::

# Code & Output {.section-slide}

## R Code Example

Standard R code blocks:

````markdown
```{{r}}
#| echo: true
set.seed(42)
x <- rnorm(100)
...
```
````

```{r}
set.seed(42)
x <- rnorm(100)
y <- 2 * x + rnorm(100, sd = 0.5)
summary(lm(y ~ x))
```

## Code with Column Output {.small-slide}

Use `#| output-location: column` to place output side-by-side.

```{r}
#| output-location: column

df <- data.frame(
  Treatment = rep(c("A", "B", "C"), each = 4),
  Response = c(23, 25, 21, 24,
               30, 32, 28, 31,
               18, 20, 17, 19)
)
df |> knitr::kable()
```

## R Plot Output

```{r}
#| fig-height: 4.5
#| fig-width: 8
library(ggplot2)
ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  theme_minimal() +
  labs(title = "Motor Trend Car Road Tests",
       x = "Weight (1000 lbs)", y = "Miles per Gallon",
       color = "Cylinders")
```

## Code with Filename {.small-slide}

Use `filename` to label code blocks:

```{r}
#| filename: "analysis.R"
#| eval: false

# Load and prepare data
library(dplyr)
data <- read.csv("experiment.csv") |>
  filter(!is.na(response)) |>
  mutate(group = factor(group))

# Fit ANOVA
model <- aov(response ~ group, data = data)
summary(model)
TukeyHSD(model)
```

# Math & Equations {.section-slide}

## LaTeX Support

**Inline math:** The sample mean is $\bar{x} = \frac{1}{n}\sum_{i=1}^{n} x_i$.

**Display math:**

$$
f(x \mid \mu, \sigma^2) = \frac{1}{\sqrt{2\pi\sigma^2}} \exp\left(-\frac{(x - \mu)^2}{2\sigma^2}\right)
$$

**Aligned equations:**

$$
\begin{align}
\hat{\beta} &= (X'X)^{-1}X'y \\
\text{Var}(\hat{\beta}) &= \sigma^2 (X'X)^{-1} \\
\hat{\sigma}^2 &= \frac{e'e}{n - p}
\end{align}
$$

# Theme Features {.section-slide}

## Emphasis Classes

Add emphasis using spans `[text]{.class}`:

| Syntax | Result | Use Case |
|--------|--------|----------|
| `[text]{.alert}` | [important note]{.alert} | Key warnings |
| `[text]{.fg}` | [highlighted]{.fg} | Accent emphasis |
| `[text]{.bg}` | [background]{.bg} | Strong emphasis |
| `[text]{.highlight}` | [key finding]{.highlight} | Highlights |
| `[text]{.note}` | [side note]{.note} | Asides |
| `[text]{.warning}` | [caution]{.warning} | Warnings |

## Standard Quarto Callouts

::: {.callout-note}
Note callouts are great for supplementary information.
:::

::: {.callout-important}
Important callouts highlight critical warnings.
:::

::: {.callout-tip}
Tip callouts suggest best practices and shortcuts.
:::

## Theme-Specific Callouts

Use divs `::: {.callout-type}` for custom boxes:

::: {.callout-example}
Consider a study with $n = 30$ subjects. The sample mean is $\bar{x} = 5.2$ with $s = 1.8$. A 95% CI for $\mu$ is $(4.53, 5.87)$.
:::

::: {.callout-question}
How does increasing the sample size affect the width of the confidence interval?
:::

::: {.callout-insight}
The CI width decreases at rate $1/\sqrt{n}$, so quadrupling the sample size halves the interval width.
:::

## Table Example {#table-example}

Standard Markdown tables with automatic striped rows:

| Source    | DF  | SS    | MS    | F     | $p$-value |
|-----------|-----|-------|-------|-------|-----------|
| Treatment | 2   | 312.0 | 156.0 | 52.00 | < .001    |
| Error     | 9   | 27.0  | 3.0   |       |           |
| Total     | 11  | 339.0 |       |       |           |

## Alignment & Buttons {.small-slide}

### Text alignment

- `{.left}` → [Left-aligned text]{.left}
- `{.center}` → [Centered text]{.center}
- `{.right}` → [Right-aligned text]{.right}

### Buttons and badges

- Button: `[[Text]{.button}](#link)`
  - [[Jump to Table Slide]{.button}](#table-example)

- Badges: `[v1.1]{.badge}`
  - [v1.1.0]{.badge} [New]{.badge-secondary}

# Diagrams {.section-slide}

## Mermaid Diagrams

```{mermaid}
flowchart LR
  A[Collect Data] --> B{Assumptions Met?}
  B -- Yes --> C[Fit Model]
  B -- No --> D[Transform Data]
  D --> B
  C --> E[Interpret Results]
```

## Graphviz Diagrams

```{dot}
digraph G {
  rankdir=LR;
  node [shape=box, style=filled, fillcolor="#F5F7FA", color="#1B365D"];
  edge [color="#4A6FA5"];
  "Raw Data" -> "Clean" -> "Explore" -> "Model" -> "Report";
}
```

# Vertical Alignment {.section-slide}

## Centered Content {.center}

This slide uses `{.center}` to vertically center all content.

Perfect for title cards or key takeaways.

**Key Finding:** The treatment effect was statistically significant ($p < .001$).

# Citations {.section-slide}

## Inline Citations

As @box1976 famously noted, all models are wrong but some are useful.

The bootstrap method [@efron1993] provides a nonparametric approach to inference. Exploratory data analysis [@tukey1977] is a crucial first step. Classical foundations include [@fisher1925] and [@neyman1933].

Modern methods span Bayesian analysis [@gelman2013], random forests [@breiman2001], regularization [@tibshirani1996], causal inference [@pearl2009; @rubin1974], machine learning [@hastie2009], and survival analysis [@cox1972].

## References

::: {#refs}
:::

# Summary {.section-slide}

## What We Covered {.small-slide}

::::: {.columns}
:::: {.column width="50%"}
### Typography

- Text formatting & lists
- Fragments & incremental
- Font sizing utilities

### Layouts

- Multi-column layouts
- Tabsets (panel-tabset)
- Slide types (small, tiny, quote)
::::

:::: {.column width="50%"}
### Code & Math

- R code execution & plots
- Column output
- LaTeX equations

### Theme Features

- Emphasis classes (6 types)
- Callouts (standard + custom)
- Buttons, badges, alignment
- Mermaid & Graphviz diagrams
::::
:::::

## Thank You {.center}

Questions?

[alias@email.com](mailto:alias@email.com)
