---
title: "dtslides UNM Theme"
subtitle: "Feature Showcase"
format:
  dtslides-unm-revealjs:
    slide-number: c/t
    chalkboard:
      theme: chalkboard
author:
  - name: Your Name
    orcid: 0000-0000-0000-0000
    email: alias@email.com
    affiliations: Department of Mathematics & Statistics
date: last-modified
---

## Example slide

### This is Heading 3

Here we have some text that may run over several lines of the slide frame,
depending on how long it is.

- This is a bullet point
- first item
    - A sub item

### Lists
1. first item
2. second item
   1. sub item

# Section Slide

## Additional theme classes {.small-slide}

### Special classes for emphasis

- `.alert` class for default emphasis, e.g. `[important note]{.alert}` ==> [important note]{.alert}.
- `.fg` class for custom color, e.g. [important note]{.fg style="--col: #e64173"}.
- `.bg` class for custom background, e.g. [important note]{.bg style="--col: #e64173"}.
- `.highlight` class for highlighting, e.g. [important note]{.highlight}.
- `.note` class for notes, e.g. [important note]{.note}.
- `.warning` class for warnings, e.g. [warning note]{.warning}.

### Cross-references

- `.button` class provides a Beamer-like button, e.g.
  - `[[Call-out Section]{.button}](#callout-sec)`
[[Call-out Section]{.button}](#callout-sec)

## Code blocks I

This is a regular code block in a slide:

```{r}
#| echo: true
# This is an R code block
x <- rnorm(100)
y <- 2 * x + rnorm(100)
summary(lm(y ~ x))
```

## Code blocks II
This is a regular code block with the cell option, `output-location: column`:

```{r}
#| echo: true
#| output-location: column
# This is an R code block
x <- rnorm(100)
y <- 2 * x + rnorm(100)
summary(lm(y ~ x))
```

## Code blocks III {.small-slide}

This is a code slide with the class `{.small-slide}`, which is useful for code-heavy slides.

```{r}
#| echo: true
N <- 12 # Number of experimental units, Step 1
# Define experimental units and treatments
experimental_units <- 1:N ## 10 experimental units
treatments <- c("A", "B", "C") ## 3 treatments, Step 2

# Repeat treatments to match the number of units. The code covers both balanced and unbalanced designs.
treatments <- rep(treatments, length.out = N) ## Step 3

# For a balanced design, we can also use:
# treatments <- rep(treatments, each = N/length(treatments))

# Shuffle (randomize) treatments randomly to assign to units, Step 4
set.seed(123) ## For reproducibility
randomized_treatments <- sample(treatments)

# Create a data frame with randomized assignments
randomization_crd <- data.frame(Unit = experimental_units, Treatment = randomized_treatments) ## Step 5
print(randomization_crd)
```

## A Long Slide

Here is an example of a slide with a long list:

1. This is item 1
2. This is item 2
3. This is item 3
4. This is item 4
5. This is item 5
6. This is item 6
7. This is item 7
8. This is item 8
9. This is item 9
10. This is item 10
11. This is item 11
12. This is item 12
13. This is item 13
14. This is item 14

## A Long Slide {.small-slide}

Here is an example of a slide with a long list and a smaller attribute class `{.small-slide}`:

1. This is item 1
2. This is item 2
3. This is item 3
4. This is item 4
5. This is item 5
6. This is item 6
7. This is item 7
8. This is item 8
9. This is item 9
10. This is item 10
11. This is item 11
12. This is item 12
13. This is item 13
14. This is item 14

## A Long Slide {.tiny-slide}

Here is an example of a slide with a long list and a tiny attribute class `{.tiny-slide}`:

1. This is item 1
2. This is item 2
3. This is item 3
4. This is item 4
5. This is item 5
6. This is item 6
7. This is item 7
8. This is item 8
9. This is item 9
10. This is item 10
11. This is item 11
12. This is item 12
13. This is item 13
14. This is item 14

## Callouts Examples {#callout-sec .tiny-slide}

Here are some examples of callout boxes:

::: {.callout-note}
This is a note callout box.
:::

::: {.callout-tip}
This is a tip callout box.
:::

::: {.callout-important}
This is an important callout box.
:::

::: {.callout-warning}
This is a warning callout box.
:::

::: {.callout-caution}
This is a caution callout box.
:::

## Table


```{r}
#| label: tab-tab1
#| echo: true
#| output-location: column

# Create a data frame
df <- data.frame(
    Name = c("Alice", "Bob", "Charlie", "David"),
    Age = c(25, 30, 35, 40),
    Height = c(5.6, 5.8, 5.9, 6.0)
)

# Print the data frame
df |> knitr::kable()

```

## Custom Call-out

::: {.callout-example}
Here’s a worked example illustrating a random intercept model.
:::

::: {.callout-question}
What changes if random slopes are included in the model?
:::

::: {.callout-insight}
This is an insight block using custom CSS.
:::